Tempo Analysis: The Sound of Teaching Music 1

### 2021-06-21 experiment-1/analysis/stats/ioi.Rmd
tweak notes
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

3. Stats packages
- [afex](https://github.com/singmann/afex) for ANOVAs

@@

### Plot
#### Line graph
- Error bars show SEM of the mean
- A dashed line represents the tempo given by a metronome (80bpm / IOI-188ms).

>>>>

3. Stats packages
- [afex](https://github.com/singmann/afex) for ANOVAs
- [rstatix](https://github.com/kassambara/rstatix) for effect sizes

@@

### Plot
#### Line graph
- Error bars show SEM of the mean.
- A dashed line represents the tempo given by a metronome (80bpm / IOI-188ms).
